\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{microtype}

% Suppress common microtype warning (harmless)
\makeatletter
\@ifundefined{MT@showhyphens@changed}{}{\let\MT@showhyphens@changed\relax}
\makeatother

% Page setup
\geometry{left=0.7in, right=0.7in, top=0.65in, bottom=0.65in}

% Hyperref
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue,
    pdfborder={0 0 0}
}

\pagestyle{empty}

% Consistent section spacing
\titleformat{\section}
{\Large\bfseries\uppercase}
{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{6pt}   % before / after section title

% Robust subheading (wraps long text automatically)
\newcommand{\resumeSubheading}[4]{
    \vspace{4pt}
    \begin{tabular*}{\textwidth}{@{} p{0.73\textwidth} @{\extracolsep{\fill}} r @{}}
        \textbf{#1} & #2 \\
        \textit{#3} & \textit{#4} \\
    \end{tabular*}
    \vspace{2pt}
}

\newcommand{\resumeProjectHeading}[1]{
    \vspace{6pt}
    \textbf{#1}\par
    \vspace{2pt}
}

\setlength{\parindent}{0pt}

\begin{document}

% Header
\begin{center}
    {\Huge\bfseries SWARALI DESHMUKH}\\[6pt]
    {\large Data Scientist | AI/ML Engineer}\\[8pt]
    Maharashtra \quad $\bullet$ \quad
    \href{mailto:swaralid42@gmail.com}{swaralid42@gmail.com} \quad $\bullet$ \quad
    +91 8956497452 \\[4pt]
    \href{https://github.com/PurpleHycinth}{GitHub} \quad $\bullet$ \quad
    \href{https://www.linkedin.com/in/swarali-deshmukh-a54597218/}{LinkedIn}
\end{center}
\vspace{10pt}

% Professional Summary
\section{Professional Summary}
AI/ML Engineer with 2+ years of applied experience building machine learning pipelines, NLP systems, and large-scale data processing workflows. Proven track record at WRI and ISRO delivering models that directly informed climate and energy policy decisions. Comfortable owning projects end-to-end — from raw 1TB+ datasets to deployed REST API inference systems. Seeking a high-impact Data Scientist / ML Engineer role at a product-first company.

% Technical Skills
\section{Technical Skills}
\begin{itemize}[leftmargin=*, label={}, itemsep=2pt, parsep=1pt]
    \item \textbf{Languages:} Python
    \item \textbf{ML / Classical:} Scikit-learn, XGBoost, Random Forest, Kernel Ridge Regression, Hyperparameter Tuning
    \item \textbf{Deep Learning:} PyTorch, TensorFlow, CNNs, Transformers, BERT, RAGs
    \item \textbf{NLP \& GenAI:} RAG Pipelines, BERT Embeddings, Named Entity Recognition, Text Classification
    \item \textbf{Data Engineering:} Pandas, NumPy, ETL Pipelines, Geospatial Data (GDAL)
    \item \textbf{Infrastructure:} Docker, REST APIs, PostgreSQL, MongoDB, Git
\end{itemize}

% Work Experience
\section{Work Experience}

\resumeSubheading
    {Junior Program Associate -- Climate, Economics \& Finance | World Resources Institute (WRI)}
    {Remote}
    {}
    {Apr 2025 -- Jul 2025}
\begin{itemize}[leftmargin=*, itemsep=3pt, parsep=1pt]
    \item Built econometric impact models in Python and R to evaluate distributional effects of carbon pricing policies across income quintiles using NSSO and HCES household survey data, adopted by WRI's India Climate Finance team.
    \item Designed and deployed automated ETL pipelines that cut data cleaning time by $\sim$60\%, enabling analysts to run policy scenario comparisons 3$\times$ faster.
    \item Led carbon emissions modelling for the Indian steel sector, producing findings referenced in 2 internal WRI policy briefs.
    \item Produced interactive data visualizations and dashboards that translated econometric outputs into accessible insights for non-technical policy stakeholders.
\end{itemize}

\resumeSubheading
    {Python Developer Intern | World Resources Institute (WRI)}
    {Remote}
    {}
    {Jul 2024 -- Jan 2025}
\begin{itemize}[leftmargin=*, itemsep=3pt, parsep=1pt]
    \item Migrated the FTT energy model from Fortran to Python, reducing codebase complexity by $\sim$40\% and enabling parallel simulation runs.
    \item Built memory-efficient data pipelines handling HCES datasets using chunked processing.
    \item Refactored 5+ legacy modeling modules into well-documented, reusable Python components with unit tests.
\end{itemize}

\resumeSubheading
    {Machine Learning Intern | Space Applications Centre (ISRO)}
    {Ahmedabad}
    {}
    {Jan 2024 -- Apr 2024}
\begin{itemize}[leftmargin=*, itemsep=3pt, parsep=1pt]
    \item Processed and fused multispectral satellite imagery with tabular agricultural datasets to train crop yield prediction models (R$^2$ = 0.84).
    \item Implemented Kernel Ridge Regression with GridSearchCV, improving forecast accuracy by $\sim$18\% over baseline.
    \item Built scalable preprocessing pipelines integrating geospatial and tabular data (reduced time from 4h to <45min).
\end{itemize}

\resumeSubheading
    {AI Intern | Anantadi Tech Pvt Ltd}
    {Pune}
    {}
    {Jun 2023 -- Aug 2023}
\begin{itemize}[leftmargin=*, itemsep=3pt, parsep=1pt]
    \item Built object detection pipelines using YOLOv8 and Detectron2 for context-aware ad placement in video frames.
    \item Benchmarked object tracking algorithms (DLIB, Norfair, GOTURN) for spatial consistency across frames.
    \item Worked in Agile sprints with twice-daily scrums and weekly presentations to leadership.
\end{itemize}

% Projects
\section{Projects}

\resumeProjectHeading{CareerWise-AI --- AI Recruitment Recommendation System}
\begin{itemize}[leftmargin=*, itemsep=3pt, parsep=1pt]
    \item Built a BERT-based resume-to-JD matching engine with cosine similarity ranking (87\% top-3 match accuracy).
    \item Developed a multi-class career path classifier using Word2Vec + XGBoost (79\% accuracy across 12 categories).
    \item Deployed a REST API (FastAPI + Docker) with React frontend for skill gap visualization.
\end{itemize}

\resumeProjectHeading{Emotion Detection from Audio}
\begin{itemize}[leftmargin=*, itemsep=3pt, parsep=1pt]
    \item Built a speech emotion classifier using MFCC, pitch, and spectral features from RAVDESS + TESS datasets (81\% accuracy).
    \item Designed a modular inference pipeline with <200ms latency.
\end{itemize}

% Education
\section{Education}

\resumeSubheading
    {M.Sc. Artificial Intelligence \& Machine Learning}
    {Expected Aug 2027}
    {Vellore Institute of Technology, Vellore}
    {SGPA: 9.46 / 10}

\resumeSubheading
    {B.Sc. Data Science}
    {2021 -- 2024}
    {Christ (Deemed to be University), Pune}
    {CGPA: 9.2 / 10}
\begin{itemize}[leftmargin=*, itemsep=2pt, parsep=1pt]
    \item Extra-Curricular Excellence Merit Award (2 consecutive years)
    \item Top 10 ranking — Data Analysis Project: Happiness Index via Twitter Data
\end{itemize}

\end{document}